---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# myscale

<!-- badges: start -->
<!-- badges: end -->

The goal of myscale is to scale the input by log or exp algorithm.

## Installation

You can install the released version of myscale from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("Leosuziqi/myscale")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(myscale)
myscale(10,"log")
```


## Brief Explanation

I made my R packages "myscale.R" with "devtools" and "usethis". The main steps are shown below:

(1) Load library and create R package to desired location
```{r}
library(devtools)
create_package("C:/STAT545b/assignment/scale")
```

(2) Create R script and wrote down my function
```{r}
use_r("myscale")
use_git()
use_mit_license("Ziqi")
```

(3) Use tools from "devtools" and "usethis" packages to document my package
```{r}
library(roxygen2)
#Code -> Insert Roxygen Skeleton
use_package("purrr")
use_vignette("myscale")
document()
```

(4) Build test file to test and check my function
```{r}
use_testthat()
# Create several conditions to check my function
test()
```
